Template for preparing your Brief Report submission to PNAS using Overleaf

### 2023-11-22 PNAS/index.Rnw
competing interest

% Please include corresponding author, author contribution and author declaration information
\authorcontributions{Please provide details of author contributions here.}
\authordeclaration{Please declare any competing interests here.}
\equalauthors{\textsuperscript{1}SVP (Author One) contributed equally to this work with HH (Author Two).}
\correspondingauthor{\textsuperscript{2}To whom correspondence should be addressed. E-mail: susan.vanderplas@unl.edu}

@@

As we develop objective algorithms and standardize laboratory procedures in forensic pattern evidence, we must remain cognizant that a single conclusion is often based on  many comparisons, either implicitly or explicitly. \hh{Algorithms, in particular, make a large number of comparisons out of a user's sight. The cross-correlation function, for example, has been suggested \citep{vorburgerApplicationsCrosscorrelationFunctions2011} as one of the first quantitative measures in response to the NAS report\citep{nas2009}, and is used in most pattern searching algorithms to find the best alignment between two sources and also evaluate the overall similarity. }
\hh{Finding the best} \svp{alignment} \hh{requires implicitly} \svp{sliding} \hh{one source across the whole length (for one-dimensional sources, such as striations) or area (for two dimensional sources, such as impression marks) of the other source and} \svp{keeping} \hh{track of the similarity measure.}

Similarly, forensic examiners visually rotate or align two pieces of evidence under comparison microscopes. When we conduct database searches, these searches often return the $N$ best matches from the database, but this requires making comparisons to all of the database entries which meet the search criteria.

>>>>

% Please include corresponding author, author contribution and author declaration information
\authorcontributions{Please provide details of author contributions here.}
\authordeclaration{The authors have no competing interests to declare.}
\equalauthors{\textsuperscript{1}SVP (Author One) contributed equally to this work with HH (Author Two).}
\correspondingauthor{\textsuperscript{2}To whom correspondence should be addressed. E-mail: susan.vanderplas@unl.edu}

@@

As we develop objective algorithms and standardize laboratory procedures in forensic pattern evidence, we must remain cognizant that a single conclusion is often based on  many comparisons, either implicitly or explicitly. \hh{Algorithms, in particular, make a large number of comparisons out of a user's sight. The cross-correlation function, for example, has been suggested \citep{vorburgerApplicationsCrosscorrelationFunctions2011} as one of the first quantitative measures in response to the NAS report\citep{nas2009}, and is used in most pattern searching algorithms to find the best alignment between two sources and also evaluate the overall similarity. }
\hh{Finding the best} \svp{alignment} \hh{requires implicitly} \svp{sliding} \hh{one source across the whole length (for one-dimensional sources, such as striations) or area (for two dimensional sources, such as impression marks) of the other source and} \svp{keeping} \hh{track of the similarity measure.}
\svp{This mirrors the forensic examination process, as examiners visually}
rotate or align two pieces of evidence under comparison microscopes.

An explicit search, in constrast, occurs when we conduct database searches.
These searches often return the $N$ best matches from the database, but this requires making comparisons to all of the database entries which meet the search criteria.
